---
title: "Policy Rules and Economic Performance"
author: "Nithin"
date: "`r format(Sys.Date(), '%d %B, %Y')`"
logo: kgp.png
output: 
  beamer_presentation:
    slide_level: 3
    includes:
      in_header: preabmle.tex            
    theme: metropolis
    latex_engine: xelatex
    template: temp_new.tex
    number_sections: true
section-titles: false
short-author: Nithin
institute: Indian Institute of Technology-Kharagpur
short-institute: IIT-KGP
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```
---

### Introduction

Debates about the conduct of monetary policy have evolved over time from “rules versus discretion” to “policy rules versus constrained discretion.”

- Is economic performance better under rules-based or discretionary monetary policy?

- Friedman (1960), Kydland and Prescott (1977), Taylor (1993a) influential in the rules vs discretion debate  
- Contrained Discretion -Bernanke (2003)  
    - Dual mandate-two goals of price stability and maximum sustainable employment
    - Any rule with positive coefficients on both gaps consistent

### Which Rule?

Given the dual mandate, which rule should **Fed** choose?

- In the literature, Optimal policy choosen by
    - Estimating a model
    - simulate the model using the estimated coefficients and disturbances
    - Minimise loss function -  inflation, output gap and change of nominal interest rates
    - Popular models- Christiano, Eichenbaum, and Evans (2005), Smets and Wouters (2007)
- This paper
    - Compare economic performance of the rules
    - Calculate **Quadratic Loss Ratio**- Loss in periods of *High Deviation* divided by Loss in periods of *Low Deviation*
    - Criterion - Loss ratio to be greater than one
    - rules with higher loss ratios are preferred to rules with lower loss ratios

### Central Results
1. Economic performance is better in low deviations periods than in high deviations periods for the vast majority of rules
1. *Inflation gap* tilting rules preferred to *Output gap*

### Methodolgy
- `r xfun::n2w(4)` benchmark rules -  equal weight on *inflation* and *unemployment*
    * Standard Taylor rule with time varying neutral interest rate
    * Taylor rule with unemployment gap
    * Taylor rule with 2% neutral interest rate
    * Taylor rule with time varying
- deviations measured as absolute deviations 
- loss calculated *`r xfun::n2w(6)`* quarters after classification 



### New slide

```{r pressure}
plot(pressure)
```


### Title
